Online analysis supplement

### 2021-11-12 index.Rmd
wip

```{r packages-settings}
#| results: 'hide'
# Packages
library(readxl)
library(ggtext)
library(janitor)
library(brms)
library(gtsummary)
library(imputeTS)
library(broom.mixed)
library(ragg)
library(scales)
library(ggh4x)
library(tidybayes)
library(naniar)
library(ggdist)
library(parameters)
library(countrycode)
library(lme4)
library(emmeans)
library(plotly)
library(knitr)
library(patchwork)
library(bayestestR)
library(lubridate)
library(haven)
library(janitor)
library(broom)
library(kableExtra)
library(ggbeeswarm)
library(ggstance)
library(sysfonts)
library(tidyverse)

@@

# Young data in wide format
gbd_wide <- gbd %>%
  pivot_wider(names_from = cause, values_from = c(val, se))
names(gbd_wide) <- str_remove(names(gbd_wide), "val_")
```

@@

```{r}
# Transform edge proportions to fit beta distribution
gbd_10 <- gbd_wide %>% 
  mutate(internet = if_else(internet == 0, .0000000001, internet)) %>% 
  mutate(internet = if_else(internet == 1, .9999999999, internet))

# Define a model of internet proportion over time
bf_int <- bf(
  internet ~ 1 + time + 
    (1 + time |c| country) +
    (1 + time |r| region), 
  family = Beta()
)

@@

@@

```{r time-correlation-anxiety}
# Get average and region
r_region_anxiety <- fit_anx %>% 
  spread_draws(
    b_Anxiety_time, 
    b_internet_time,
    r_region__Anxiety[region, term],
    r_region__internet[region, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by replacing dot with line break
  mutate(region = str_replace(region, "\\.", "\n"))

# Then country
r_country_anxiety <- fit_anx %>% 
  spread_draws(
    r_country__Anxiety[country, term],
    r_country__internet[country, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by taking labels from original names
  mutate(
    country = factor(
      country, 
      labels = sort(unique(fit_anx$data$country))
    )
  ) %>% 
  left_join(distinct(gbd, region, country))

# Calculate country coefficients
country_anxiety <- left_join(r_country_anxiety, r_region_anxiety) %>% 
  mutate(
    internet = b_internet_time + r_region__internet + r_country__internet,
    anxiety = b_Anxiety_time + r_region__Anxiety + r_country__Anxiety
  ) %>% 
  group_by(country, region) %>% 
  median_qi(internet, anxiety)

country_anxiety_ellipse <- spread_draws(
  fit_anx,
  b_Anxiety_time, b_internet_time,
  cor_country__internet_time__Anxiety_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_country__internet_time__Anxiety_time, 
        y = b_internet_time, 
        z = b_Anxiety_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

region_anxiety_ellipse <- spread_draws(
  fit_anx,
  b_Anxiety_time, b_internet_time,
  cor_region__internet_time__Anxiety_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_region__internet_time__Anxiety_time, 
        y = b_internet_time, 
        z = b_Anxiety_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

country_anxiety_cor <- fit_anx %>%
  as_draws_df(
    variable = c(
      "cor_country__internet_time__Anxiety_time",
      "cor_region__internet_time__Anxiety_time"
    ),
    regex = TRUE
  ) %>% 
  as_tibble()
country_anxiety_result <- country_anxiety_cor %>%   
  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))

p_cor_country_anx <- country_anxiety %>% 
  ggplot(aes(internet, anxiety)) +
  # geom_path(
  #   data = region_anxiety_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
  # ) +
  # geom_path(
  #   data = country_anxiety_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
  # ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
  scale_x_continuous(
    "Linear internet trend",
    breaks = pretty_breaks()
  ) +
  scale_y_continuous(
    "Linear anxiety trend",
    breaks = pretty_breaks()
  ) +
  geom_richtext(
    data = country_anxiety_result %>% 
      filter(variable == "cor_country__internet_time__Anxiety_time"),
    aes(x = -Inf, y = Inf, label = result),
    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  ) +
  theme(aspect.ratio = 1)
```

@@

# Fit models in background (need 12 cores)
fit_anx <- brm(
  bf_int + bf_anx + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-internet-anxiety",
  chains = 4,
  cores = 4,
  iter = 1000, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
fit_dep <- brm(
  bf_int + bf_dep + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-internet-depression",
  chains = 4,
  cores = 4,
  iter = 1000, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
fit_sel <- brm(
  bf_int + bf_sel + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-internet-selfharm",
  chains = 4,
  cores = 4,
  iter = 1000, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
fits_brm_internet_main <- tibble(
  outcome = c("Anxiety", "Depression", "Selfharm"),
  fit = list(fit_anx, fit_dep, fit_sel)
)
```

@@

Different levels

```{r}
# Get average and region
r_selfharm <- fit_sel %>% 
  spread_draws(
    b_Selfharm_i1_cw, 
    r_region__Selfharm[region, term]
  ) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  # Fix names by replacing dot with line break
  mutate(region = str_replace(region, "\\.", "\n"))

fit_sel %>% 
  spread_draws(
    r_country__Selfharm[country, term]
    )

# Calculate country coefficients
r_selfharm <- r_selfharm %>% 
  mutate(
    b_average = b_Selfharm_i1_cw,
    b_region = b_average + r_region__Selfharm,
    b_country = b_region + r_country__Selfharm
  )

r_selfharm %>% 
  distinct(.draw, b_average) %>% 
  mutate(region = "Average") %>% 
  ggplot(aes(b_average, region)) +
  stat_halfeye(size = 1, fill = "dodgerblue4") +
  stat_halfeye(
    data = r_selfharm %>% 
      distinct(.draw, region, b_region),
    aes(b_region),
    size = 1, fill = "dodgerblue1"
  ) +
  geom_point(
    data = 
  )
r_selfharm %>% 
  group_by(region, country) %>% 
  median_qi(b_country)
```

@@

# Fit models in background (need 12 cores)
job::job({
  fit_anx <- brm(
    bf_anx,
    data = gbd_wide,
    file = "output/brm-gbd-time-internet-anxiety-int2",
    chains = 4,
    cores = 4,
    iter = 1200, warmup = 600, refresh = 10,
    threads = 1,
    control = list(adapt_delta = .9)
  )
}, title = "Fitting brms anxiety")
job::job({
  fit_dep <- brm(
    bf_dep,
    data = gbd_wide,
    file = "output/brm-gbd-time-internet-depression-int2",
    chains = 4,
    cores = 4,
    iter = 1200, warmup = 600, refresh = 10,
    threads = 1,
    control = list(adapt_delta = .9)
  )
}, title = "Fitting brms depression")
fit_sel <- brm(
  bf_sel,
  data = gbd_wide,
  file = "output/brm-gbd-time-internet-selfharm-int2",
  chains = 4,
  cores = 4,
  iter = 1200, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
```

###### Plot: Average effects of time

```{r eval = FALSE}
fixef(fit_gbd_time) %>%
  as.data.frame() %>% 
  rownames_to_column("Parameter") %>% 
  as_tibble()

## Model 2: Associations

This model expands the above to add internet adoption as a predictor.

#### Figure

```{r}
gbd %>% 
  ggplot(
    aes(
      x = i1_cw/10, 
      y = val, 
      col = region, fill = region
    )
  ) +
  geom_point(size = .25, alpha = .1) +
  stat_smooth(method = "lm", alpha = .2, size = .3) +
  # stat_summary(fun = mean, geom = "line", size = .25) +
  facet_grid(Cause~region, scales = "free_y") +
  theme(legend.position = "none")
```

```{r fit-gbd-internet-lme4}
# These take about 1-3 hours each
# run in parallel in background jobs
# recommended to conduct this in interactive mode (rstudio)
file_path <- "output/lme4-gbd-internet.rds"
if (!file.exists(file_path)) {
  library(job)
  job({fit_anx <- lmer(
    Anxiety ~ 1 + time * sex * age + i1_cw * sex * age + i1_cb +
      (1 + time * sex * age + i1_cw * sex * age | region) +
      (1 + time * sex * age + i1_cw * sex * age | country),
    data = gbd_wide
  )}, title = "Anxiety internet (lmer)")
  job({fit_dep <- lmer(
    Depression ~ 1 + time * sex * age + i1_cw * sex * age + i1_cb +
      (1 + time * sex * age + i1_cw * sex * age | region) +
      (1 + time * sex * age + i1_cw * sex * age | country),
    data = gbd_wide
  )}, title = "Depression internet (lmer)")
  job({fit_sel <- lmer(
    Selfharm ~ 1 + time * sex * age + i1_cw * sex * age + i1_cb +
      (1 + time * sex * age + i1_cw * sex * age | region) +
      (1 + time * sex * age + i1_cw * sex * age | country),
    data = gbd_wide
  )}, title = "Self harm internet (lmer)")
  fits_lmer <- distinct(gbd, cause) %>% 
    mutate(fit = list(fit_anx, fit_dep, fit_sel))
  write_rds(fits_lmer, file_path)
} else {fits_lmer <- read_rds(file_path)}
```

```{r}
fits_lmer %>% 
  mutate(out = map(fit, ~tidy(., conf.int = TRUE))) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  filter(term == "i1_cw")
```

```{r fit-gbd-internet-brms, eval = FALSE}
# bf_gbd_internet <- bf(
#   mvbind(
#     val_Depression,
#     val_Anxiety,
#     val_Self_harm
#   ) ~ 1 + Time + i1_cw + i1_cb +
#     (1 + Time + i1_cw || region)
#   (1 + Time + i1_cw || country)
# ) +
#   set_rescor(FALSE)
# 
# fit_gbd_internet <- brm(
#   bf_gbd_internet,
#   gbd_y_w,
#   file = "output/brm-gbd-internet-mv",
#   chains = 5,
#   cores = 5,
#   iter = 300, warmup = 150, refresh = 10,
#   threads = 2,
#   control = list(adapt_delta = .9, max_treedepth = 15)
# )

bf_gbd_internet_demos <- bf(
  mvbind(
    Depression,
    Anxiety,
    Selfharm
  ) ~ 1 + time * sex * age + i1_cw * sex * age + i1_cb +
    (1 + time * sex * age + i1_cw * sex * age | country)
) +
  set_rescor(FALSE)

p <- prior(normal(0, 3), class = b, resp = Anxiety) +
  prior(normal(0, 3), class = b, resp = Depression) +
  prior(normal(0, 3), class = b, resp = Selfharm) +
  prior(student_t(7, 0, 1), class = sd, resp = Anxiety) +
  prior(student_t(7, 0, 1), class = sd, resp = Depression) +
  prior(student_t(7, 0, 1), class = sd, resp = Selfharm)

job::job({fit_gbd_internet_demos <- brm(
  bf_gbd_internet_demos,
  gbd_wide,
  prior = p,
  file = "output/brm-gbd-internet-mv-demos",
  chains = 5,
  cores = 5,
  iter = 450, warmup = 300, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9, max_treedepth = 15)
)}, title = "brms internet")
```

>>>>

```{r packages-settings}
#| results: 'hide'
# Packages
library(readxl)
library(ggtext)
library(janitor)
library(brms)
library(gtsummary)
library(ellipse)
library(imputeTS)
library(broom.mixed)
library(ragg)
library(scales)
library(ggh4x)
library(tidybayes)
library(naniar)
library(ggdist)
library(parameters)
library(countrycode)
library(lme4)
library(emmeans)
library(plotly)
library(knitr)
library(patchwork)
library(bayestestR)
library(lubridate)
library(haven)
library(janitor)
library(broom)
library(kableExtra)
library(ggbeeswarm)
library(ggstance)
library(sysfonts)
library(tidyverse)

@@

# Young data in wide format
gbd_wide <- gbd %>%
  pivot_wider(names_from = cause, values_from = c(val, se))
names(gbd_wide) <- str_remove(names(gbd_wide), "val_")

# Transform edge proportions to fit beta distribution
gbd_10 <- gbd_wide %>% 
  mutate(internet = if_else(internet == 0, .0000000001, internet)) %>% 
  mutate(internet = if_else(internet == 1, .9999999999, internet))
```

@@

```{r}
# Define a model of internet proportion over time
bf_int <- bf(
  internet ~ 1 + time + 
    (1 + time |c| country) +
    (1 + time |r| region), 
  family = Beta()
)

@@

A figure of coefficients

```{r}
anx_draws <- spread_draws(
  fit_anx, 
  b_Anxiety_time, r_region__Anxiety[region, term] | region
) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Anxiety_time) %>% 
  mutate(outcome = "Anxiety")
dep_draws <- spread_draws(
  fit_dep, 
  b_Depression_time, r_region__Depression[region, term] | region
) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Depression_time) %>% 
  mutate(outcome = "Depression")
sel_draws <- spread_draws(
  fit_sel, 
  b_Selfharm_time, r_region__Selfharm[region, term] | region
) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Selfharm_time) %>% 
  mutate(outcome = "Selfharm")

p_time_main_coefs <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
  mutate(across(Africa:Southern.Asia, ~.+Average)) %>% 
  pivot_longer(Average:Southern.Asia, names_to = "region") %>% 
  mutate(region = fct_relevel(factor(region), "Average")) %>% 
  mutate(outcome = factor(outcome)) %>% 
  mutate(is_average = region == "Average") %>% 
  mutate(region = str_replace(region, "\\.", " ")) %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.5, .9)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_x_continuous("Linear trend", breaks = pretty_breaks()) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels"
  ) +
  facet_wrap("outcome", nrow = 1, scales = "free_x") +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )
p_time_main_coefs
```

###### Correlations

@@

```{r time-correlation-anxiety}
# Function to wrangle draws at multiple levels and create scatterplots + ellipses
draw_scatterplot <- function(fit, beta, r_region, r_country, sd_country, cor_country) {
  # Get average and region-specific slopes
  r_region_draws <- fit %>% 
    spread_draws(
      {{beta}}, 
      b_internet_time,
      {{r_region}}[region, term],
      r_region__internet[region, term]
    ) %>% 
    filter(term == "time") %>% 
    ungroup() %>% 
    # Fix names by replacing dot with line break
    mutate(region = str_replace(region, "\\.", "\n"))

  # Then country
  r_country_draws <- fit %>% 
    spread_draws(
      {{r_country}}[country, term],
      r_country__internet[country, term]
    ) %>% 
    filter(term == "time") %>% 
    ungroup() %>% 
    # Fix names by taking labels from original names
    mutate(
      country = factor(
        country, 
        labels = sort(unique(fit$data$country))
      )
    ) %>% 
    left_join(distinct(gbd, region, country))

  # Calculate country coefficients
  country_coefs <- left_join(r_country_draws, r_region_draws) %>% 
    mutate(
      internet = b_internet_time + r_region__internet + r_country__internet,
      outcome = {{beta}} + {{r_region}} + {{r_country}}
    ) %>% 
    group_by(country, region) %>% 
    median_qi(internet, outcome)

  # Create country ellipse data
  country_ellipse <- spread_draws(
    fit,
    {{beta}}, 
    b_internet_time,
    {{sd_country}},
    sd_country__internet_time,
    {{cor_country}}, 
    ndraws = 100
  ) %>% 
    rename(
      cor = {{cor_country}}, 
      sd_outcome = {{sd_country}},
      sd_i = sd_country__internet_time,
      b_outcome = {{beta}},
      b_i = b_internet_time
    ) %>% 
    mutate(
      e = pmap(
        list(cor, sd_outcome, sd_i, b_outcome, b_i), 
        function(cor, sd_a, sd_i, b_a, b_i) 
          ellipse(
            cor, 
            scale = c(sd_i, sd_outcome), 
            centre = c(b_i, b_outcome), 
            level = .90
          ) %>% 
          as_tibble()
      )
    ) %>% 
    unnest(e)

  # Correlation
  country_cor_result <- spread_draws(fit, {{cor_country}}) %>% 
    median_qi(.width = .90) %>% 
    mutate(across(where(is.numeric), ~round(., 2))) %>%
    {str_glue("{.[,1]} [{.[,2]}, {.[,3]}]")}

  # Plot
  country_coefs %>% 
    ggplot(aes(internet, outcome)) +
    geom_path(
      data = country_ellipse,
      aes(x = x, y = y), 
      alpha = .2, size = .1, col = "dodgerblue1"
    ) +
    geom_vline(xintercept = 0, lty = 2, size = .2) +
    geom_hline(yintercept = 0, lty = 2, size = .2) +
    geom_point(col = "dodgerblue1", size = 1, alpha = .5) +
    scale_x_continuous(
      "Internet trend",
      breaks = pretty_breaks()
    ) +
    scale_y_continuous(
      breaks = pretty_breaks()
    ) +
    annotate(
      "text",
      x = Inf, y = Inf, label = country_cor_result,
      size = 4, vjust = 1.5, hjust = 1.05, color = "dodgerblue4",
      family = Font
    )
}
```

```{r}
p_cor_country_anx <- draw_scatterplot(
  fit_anx, 
  b_Anxiety_time, 
  r_region__Anxiety, 
  r_country__Anxiety,
  sd_country__Anxiety_time,
  cor_country__internet_time__Anxiety_time
) + labs(y = "Anxiety trend")
p_cor_country_dep <- draw_scatterplot(
  fit_dep, 
  b_Depression_time, 
  r_region__Depression, 
  r_country__Depression,
  sd_country__Depression_time,
  cor_country__internet_time__Depression_time
) + labs(y = "Depression trend")
p_cor_country_sel <- draw_scatterplot(
  fit_sel, 
  b_Selfharm_time, 
  r_region__Selfharm, 
  r_country__Selfharm,
  sd_country__Selfharm_time,
  cor_country__internet_time__Selfharm_time
) + labs(y = "Self-harm trend")
```

```{r}
p_time_main_correlations <- p_cor_country_anx |
  p_cor_country_dep |
  p_cor_country_sel

(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
  p_time_main_correlations

p_time_main_coefs /
  p_time_main_correlations
```

@@

# Fit models in background (need 12 cores)
job::job({fit_anx <- brm(
  bf_anx,
  data = gbd_10,
  file = "output/brm-gbd-time-internet-anxiety",
  chains = 4,
  cores = 4,
  iter = 1200, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)})
job::job({fit_dep <- brm(
  bf_dep,
  data = gbd_10,
  file = "output/brm-gbd-time-internet-depression",
  chains = 4,
  cores = 4,
  iter = 1200, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)})
fit_sel <- brm(
  bf_sel,
  data = gbd_10,
  file = "output/brm-gbd-time-internet-selfharm",
  chains = 4,
  cores = 4,
  iter = 1000, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
fits_brm_internet_main <- tibble(
  outcome = c("Anxiety", "Depression", "Selfharm"),
  fit = list(fit_anx, fit_dep, fit_sel)
)
```

@@

###### Fitted lines

Plot of fitted lines

```{r}
draws_country_anx <- epred_draws(
  fit_anx, 
  gbd_wide %>% 
    filter(country %in% sort(unique(fit_anx$data$country))) %>% 
    mutate(time = 0),
  re_formula = ~(1 + time + sex + age + i1_cw |r| region) + 
    (1 + time + sex + age + i1_cw |c| country), 
  ndraws = 100,
  resp = "Anxiety"
)

draws_country_dep <- epred_draws(
  fit_dep, 
  gbd_wide %>% 
    filter(country %in% sort(unique(fit_dep$data$country))) %>% 
    mutate(time = 0),
  re_formula = ~(1 + time + sex + age + i1_cw |r| region) + 
    (1 + time + sex + age + i1_cw |c| country), 
  ndraws = 30,
  resp = "Depression"
)

draws_country_sel <- epred_draws(
  fit_sel, 
  gbd_wide %>% 
    filter(country %in% sort(unique(fit_sel$data$country))) %>% 
    mutate(time = 0),
  re_formula = ~(1 + time + sex + age + i1_cw |r| region) + 
    (1 + time + sex + age + i1_cw |c| country), 
  ndraws = 30,
  resp = "Selfharm"
)

draws_region_anx <- epred_draws(
  fit_anx, 
  distinct(fit_anx$data, region, sex, age, i1_cb) %>% 
    group_by(region) %>% 
    mutate(i1_cb = mean(i1_cb, na.rm = T)) %>% 
    crossing(i1_cw = seq(-4, 4, length = 10)) %>% 
    mutate(time = 0),
  re_formula = ~(1 + time + sex + age + i1_cw |r| region),
  ndraws = 30,
  resp = "Anxiety"
) %>% 
  mutate(outcome = "Anxiety")

draws_region_dep <- epred_draws(
  fit_dep, 
  distinct(fit_dep$data, region, sex, age, i1_cb) %>%
    group_by(region) %>% 
    mutate(i1_cb = mean(i1_cb, na.rm = T)) %>% 
    crossing(i1_cw = seq(-4, 4, length = 10)) %>% 
    mutate(time = 0),
  re_formula = ~(1 + time + sex + age + i1_cw |r| region),
  ndraws = 30,
  resp = "Depression"
) %>% 
  mutate(outcome = "Depression")

draws_region_sel <- epred_draws(
  fit_sel, 
  distinct(fit_sel$data, region, sex, age, i1_cb) %>% 
    group_by(region) %>% 
    mutate(i1_cb = mean(i1_cb, na.rm = T)) %>% 
    crossing(i1_cw = seq(-4, 4, length = 10)) %>% 
    mutate(time = 0),
  re_formula = ~(1 + time + sex + age + i1_cw |r| region),
  ndraws = 30,
  resp = "Selfharm"
) %>% 
  mutate(outcome = "Self-harm")

draws_region <- bind_rows(
  draws_region_anx, draws_region_dep, draws_region_sel
) %>% 
  group_by(outcome, region, i1_cw) %>% 
  median_qi(.epred)

bind_rows(
  draws_country_anx %>% mutate(outcome = "Anxiety"),
  draws_country_dep %>% mutate(outcome = "Depression"),
  draws_country_sel %>% mutate(outcome = "Self-harm")
) %>% 
  group_by(country) %>% 
  # mutate(i1_cw2 = i1_cw/10 + mean(internet, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot(aes(i1_cw, .epred)) +
  scale_x_continuous(
    "Previous year's internet adoption relative to country average in 2000-2020",
    breaks = pretty_breaks(3),
    labels = function(x) percent(x/10, 1)
  ) +
  scale_y_continuous(
    "Estimated rate",
    breaks = pretty_breaks()
  ) +
  geom_ribbon(
    data = draws_region,
    aes(ymin = .lower, ymax = .upper),
    fill = "dodgerblue4", size = .6, alpha = .2
  ) +
  geom_line(
    data = draws_region,
    col = "dodgerblue4", size = .6
  ) +
  stat_summary(
    fun=mean, geom = "line",
    aes(group = country), 
    size = .4, alpha = .25, col = "dodgerblue1"
  ) +
  facet_grid(outcome~region, scales = "free_y") +
  theme(panel.spacing = unit(2, "pt"))
```

###### Forest plots

figure of coefficients forest plot

```{r}
anx_draws <- spread_draws(
  fit_anx, 
  b_Anxiety_i1_cw, r_region__Anxiety[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Anxiety_i1_cw) %>% 
  mutate(outcome = "Anxiety")
dep_draws <- spread_draws(
  fit_dep, 
  b_Depression_i1_cw, r_region__Depression[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Depression_i1_cw) %>% 
  mutate(outcome = "Depression")
sel_draws <- spread_draws(
  fit_sel, 
  b_Selfharm_i1_cw, r_region__Selfharm[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Selfharm_i1_cw) %>% 
  mutate(outcome = "Selfharm")

results_text <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
  group_by(outcome) %>% 
  summarise(parameters(cur_data()[-c(1:3)])) %>% 
  mutate(region = str_replace(Parameter, "\\.", " ")) %>% 
  mutate(is_average = region == "Average") %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  mutate(across(Median:CI_high, ~format(round(., 2), nsmall = 2)))

p_internet_main_coefs <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
  mutate(across(Africa:Southern.Asia, ~.+Average)) %>% 
  pivot_longer(Average:Southern.Asia, names_to = "region") %>% 
  mutate(region = fct_relevel(factor(region), "Average")) %>% 
  mutate(outcome = factor(outcome)) %>% 
  mutate(is_average = region == "Average") %>% 
  mutate(region = str_replace(region, "\\.", " ")) %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.5, .9)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_y_discrete(expand = expansion(c(0.01, .1))) +
  scale_x_continuous(
    "Estimated association to internet adoption", 
    breaks = pretty_breaks(), 
    expand = expansion(c(.1, .5))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels", height = .75
  ) +
  geom_text(
    data = results_text, alpha = 1, size = 2.75, hjust = 1, vjust = -0.2,
    aes(
      x = Inf, 
      label = str_glue("{Median} [{CI_low}, {CI_high}]")
    )
  ) +
  facet_wrap("outcome", nrow = 1, scales = "free_x") +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )

(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
  p_internet_main_coefs
```

@@

# Fit models
fit_anx <- brm(
  bf_anx,
  data = gbd_wide,
  file = "output/brm-gbd-time-internet-anxiety-int2",
  chains = 4,
  cores = 4,
  iter = 1200, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
fit_dep <- brm(
  bf_dep,
  data = gbd_wide,
  file = "output/brm-gbd-time-internet-depression-int2",
  chains = 4,
  cores = 4,
  iter = 1200, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
fit_sel <- brm(
  bf_sel,
  data = gbd_wide,
  file = "output/brm-gbd-time-internet-selfharm-int2",
  chains = 4,
  cores = 4,
  iter = 1200, warmup = 600, refresh = 10,
  threads = 1,
  control = list(adapt_delta = .9)
)
fits_brm_internet_interactions <- tibble(
  outcome = c("Anxiety", "Depression", "Selfharm"),
  fit = list(fit_anx, fit_dep, fit_sel)
)
```

```{r}
fits_brm_internet_interactions %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  # filter(str_detect(variable, "_i1_cw|b$")) %>% 
  kbl(digits = 3) %>% 
  kable_minimal(full_width = FALSE)
```

Model comparisons

```{r}
tmp <- left_join(
  fits_brm_internet_main,
  fits_brm_internet_interactions %>% rename(fit_i = fit)
) %>% 
  mutate(comp = map2(fit, fit_i, waic))

###### Forest plots

figure of coefficients forest plot

```{r}
anx_draws <- spread_draws(
  fit_anx, 
  b_i1_cw, r_region[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_i1_cw) %>% 
  mutate(outcome = "Anxiety")
dep_draws <- spread_draws(
  fit_dep, 
  b_i1_cw, r_region[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_i1_cw) %>% 
  mutate(outcome = "Depression")
sel_draws <- spread_draws(
  fit_sel, 
  b_i1_cw, r_region[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_i1_cw) %>% 
  mutate(outcome = "Selfharm")

results_text <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
  group_by(outcome) %>% 
  summarise(parameters(cur_data()[-c(1:3)])) %>% 
  mutate(region = str_replace(Parameter, "\\.", " ")) %>% 
  mutate(is_average = region == "Average") %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  mutate(across(Median:CI_high, ~format(round(., 2), nsmall = 2)))

p_internet_main_coefs <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
  mutate(across(Africa:Southern.Asia, ~.+Average)) %>% 
  pivot_longer(Average:Southern.Asia, names_to = "region") %>% 
  mutate(region = fct_relevel(factor(region), "Average")) %>% 
  mutate(outcome = factor(outcome)) %>% 
  mutate(is_average = region == "Average") %>% 
  mutate(region = str_replace(region, "\\.", " ")) %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(expand = expansion(c(0.01, .1))) +
  scale_x_continuous(
    "Magnitude of association between internet adoption and well-being", 
    breaks = pretty_breaks(), 
    expand = expansion(c(.1, .5))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels", 
    height = .75, adjust = 1.5
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.9),
    interval_size = .5,
    point_size = 1.5,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, -.025)
  ) +
  geom_text(
    data = results_text, alpha = 1, size = 2.75, hjust = 1, vjust = -0.2,
    aes(
      x = Inf, 
      label = str_glue("{Median} [{CI_low}, {CI_high}]")
    )
  ) +
  facet_wrap("outcome", nrow = 1, scales = "free_x") +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )

(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
  p_internet_main_coefs
```

Between country?

```{r}
pred_data <- gbd_wide %>% 
  distinct(region, country, sex, age, i1_cb, i1_cw = 0, time = 0) %>% 
  filter(country %in% sort(unique(fit_anx$data$country)))

tmp <- epred_draws(
  fit_anx, pred_data, re_formula = 
    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country)
)

tmp %>% 
  group_by(region, country, i1_cb) %>% 
  summarise(mean(.epred))

conditional_effects(fit_anx, "i1_cb")

gbd_wide %>% 
  group_by(country) %>% 
  summarise(i1_cb = unique(i1_cb), anx = mean(Anxiety)) %>% 
  ggplot(aes(i1_cb, anx)) +
  geom_point() +
  stat_smooth()
